quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-18 paper-quollr.Rmd
Updated axis text size

scurve_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "a1", cex = 1)

@@

scurve_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "a2", cex = 1)

@@

scurve_proj_umap_model3 <- plot_proj(
  proj_obj = proj_obj3,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "a3", cex = 1)

@@

scurve_proj_umap_model4 <- plot_proj(
  proj_obj = proj_obj4,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 3,
  is_category = FALSE) +
  interior_annotation(label = "a4", cex = 1) 
```

>>>>

scurve_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a1", cex = 1)

@@

scurve_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a2", cex = 1)

@@

scurve_proj_umap_model3 <- plot_proj(
  proj_obj = proj_obj3,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a3", cex = 1)

@@

scurve_proj_umap_model4 <- plot_proj(
  proj_obj = proj_obj4,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a4", cex = 1) 
```
